---
title: "Visualization"
subtitle: "Part I"
author: "Fenglin Xie"
date: "2025-09-25"
output: github_document
---

```{r}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
```

Import the weather data
```{r}
data("weather_df")
```

Making the first plot

```{r}
ggplot(data = weather_df, mapping = aes(x = tmin, y = tmax)) +
  geom_point()
```

也可以这样

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) +
  geom_point()
```


```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```


```{r}
ggp_weather_scatterplot = 
  weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()

ggp_weather_scatterplot
```

check that some rows are missing.

```{r}
weather_df |> 
  filter(is.na(tmax))
```


## Fancier scatterplot!

##smooth得出来的error bound基本不可信，所以用se = FALSE去掉它
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE)
```


where you define aesthetics can matter 

##没听懂？？？

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name, size = prcp), alpha = 0.3) +
  geom_smooth(se = FALSE)
```


use faceting real quick

row ~ column
. ~ name :三列name
name ~ . :三行name

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(color = name), alpha = 0.3, size = 0.3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


Let's make a somewhat more interesting scatterplot

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
  geom_point(aes(size = prcp),alpha = 0.3) +
  geom_smooth(se = FALSE) +
  facet_grid(. ~ name)
```


LA plot

```{r}
weather_df =
  filter(name == "CentralPark_NY") |> 
  mutate(
    tmax_fahr = tmax * (9/5) + 32,
    tmin_fahr = tmin * (9/5) + 32
  ) |> 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
   geom_point() +
   geom_smooth(se = FALSE, method = "lm")
```


## Small thing

换顺序会变换overlap的顺序：线在上--点在上
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
#  geom_point(alpha = 0.3) +
  geom_smooth(se = FALSE)


weather_df |> 
  ggplot(aes(x = tmin, y = tmax, color = name, shape = name)) +
  geom_smooth(se = FALSE) +
  geom_point(alpha = 0.3)
```
```
```

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex()
```


```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "purple")
```

##可以去网上查颜色编号
```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(color = "#086bdf")
```


```{r}
weather_df |> 
  ggplot(aes(x = tmin)) +
  geom_histogram(color = "white", fill = "red")
```


```{r}
weather_df |> 
  ggplot(aes(x = tmin, colour = name)) +
  geom_histogram()

weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram()
```
overlapping is a problem somtimes--solve it
maybe facet?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_histogram() +
  facet_grid(name ~ .)
```

maybe a density plot?

```{r}
weather_df |> 
  ggplot(aes(x = tmin, fill = name)) +
  geom_density(alpha = 0.2)
```

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin)) +
  geom_boxplot(aes(fill = name))
```


violin plots--symmetrical

```{r}
weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()
  
```


ridge plot

```{r}
weather_df |> 
  ggplot(aes(x = tmin, y = name, fill = name)) +
  geom_density_ridges()
```



LA
```{r}
weather_df |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = 0.3)

weather_df |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_histogram(alpha = 0.2) +
  facet_grid(name ~ .)

weather_df |> 
  filter(prcp > 5, prcp < 1000) |> 
  ggplot(aes(x = prcp, fill = name)) +
  geom_density(alpha = 0.3)
```

## Saving and embedding plots

saving plots
```{r}
ggp_weather_violin =
  weather_df |> 
  ggplot(aes(x = name, y = tmin, fill = name)) +
  geom_violin()

ggp_weather_violin

ggsave("plots/violin_plot.pdf", ggp_weather_violin, width = 8, height = 6)


```

##补笔记
embedding plots
```{r}

```

